---
title: "Tutorial for urlshorteneR"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial for urlshorteneR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
This package wrapps [Bit.ly](https://www.bitly.com) & [Goo.gl](https://goo.gl) API. In order to begin shortening URLs and downloading usefull statistics, there is one requirement, which is to authenticate using OAUTH2 for each service (of course, if you need both of them) 
  
## Authentication

See `??googl_auth`. Please do not use my API Keys as they may not work properly. 
  
# Bit.ly
  
## An Example for User Metrics
  
Official API documentation <http://dev.bitly.com/user_metrics.html>.
  
Method below returns my most-clicked Bit.ly links (ordered by number of clicks) in a given time period.
  
```{r}
library(urlshorteneR)
# print(getwd())
# 
# btoken_path <- file.path("..", "tests", "testthat", "bitly_token.rds")
# gtoken_path <- file.path("..", "tests", "testthat", "googl_token.rds")
# 
bitly_token <- readRDS("../tests/testthat/bitly_token.rds")
googl_token <- readRDS("../tests/testthat/googl_token.rds")

# You should register a new pair of keys yourself. DO NOT USE MINE as this may not work. 
# bitly_token <- bitly_auth(key = "be03aead58f23bc1aee6e1d7b7a1d99d62f0ede8", secret = "b7e4abaf8b26ec4daa92b1e64502736f5cd78899")

bitly_UserMetricsPopularLinks(unit = "month", units = -1, limit = 100)
```


## An Example for Link Metrics

Official API documentation <http://dev.bitly.com/link_metrics.html>.

This returns users, who have encoded `http://bit.ly/DPetrov` link sorted by the number of clicks on each encoding user's link.

```{r}
bitly_LinksMetricsEncodersByCount(link = "http://bit.ly/DPetrov", my_network = "false", limit = 100)
```


## An Example for User Info/History

Official API documentation <http://dev.bitly.com/user_info.html>. 

The first method returns an information about myself, whereas the second one returns a list of tracking domains I have configured (I have none).

```{r}
bitly_UserInfo()

bitly_UserTrackingDomains()
```


## An Example for Domains

Official API documentation <http://dev.bitly.com/domains.html>. 

This will query whether a given domain is a valid Bit.ly PRO domain (nyti.ms is). 

```{r}
bitly_IsProDomain(domain = "nyti.ms")
```

# Goo.gl

```{r}
#
# googl_auth(key = "806673580943-78jdskus76fu7r0m21erihqtltcka29i.apps.googleusercontent.com", secret = "qItL-PZnm8GFxUOYM0zPVr_t")
#
g2 <- googl_LinksShorten(longUrl = "https://developers.google.com/url-shortener/v1/url/insert")
g2
g1 <- googl_LinksExpand(shortUrl = "http://goo.gl/vM0w4", showRequestURL = F)
g1
```

# Is.gd

```{r}
isgd_LinksShorten(longUrl = "http://debil.cz/", showRequestURL = TRUE)
```


-------------

### What has (not) been implemented for Bit.ly:

Based on <http://dev.bitly.com/>

<http://dev.bitly.com/user_info.html>  | Implemented Yes/No
------------- | -------------
/v3/oauth/app  | (**NOT**, see below)
/v3/user/info  | Yes
/v3/user/link_history | Yes
/v3/user/network_history  | **NOT**
/v3/user/tracking_domain_list  | Yes

<http://dev.bitly.com/link_metrics.html>  | Implemented Yes/No
------------- | -------------
/v3/link/clicks  | Yes
/v3/link/countries  | Yes
/v3/link/encoders  | Yes
/v3/link/encoders_by_count  | Yes
/v3/link/encoders_count  | Yes
/v3/link/referrers  | Yes
/v3/link/referrers_by_domain  | Yes
/v3/link/referring_domains  | Yes


<http://dev.bitly.com/user_metrics.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/user/clicks  | Yes 
/v3/user/countries  | Yes 
/v3/user/popular_earned_by_clicks  | **NOT**  | Yes
/v3/user/popular_earned_by_shortens  | **NOT**  | Yes
/v3/user/popular_links  | Yes
/v3/user/popular_owned_by_clicks  | **NOT**  | Yes
/v3/user/popular_owned_by_shortens | **NOT**  | Yes
/v3/user/referrers  | Yes
/v3/user/referring_domains | Yes
/v3/user/shorten_counts | Yes


<http://dev.bitly.com/domains.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/bitly_pro_domain  | Yes | No
/v3/user/tracking_domain_clicks  | **NOT** | Yes (cannot do unless sombody helps)
/v3/user/tracking_domain_shorten_counts  | **NOT** | Yes (cannot do unless sombody helps)


<http://dev.bitly.com/links.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/expand  | Yes 
/v3/info  | Yes 
/v3/link/lookup  |  Yes
/v3/shorten  | Yes  
/v3/user/link_edit  | **NOT**  | No
/v3/user/link_lookup  | **NOT**  | No
/v3/user/link_save | **NOT**  | No
/v3/user/save_custom_domain_keyword | **NOT**  | Yes

- <http://dev.bitly.com/nsq.html>  
    + None endpoints are implemented here, logically. This is only for the [NSQ](http://nsq.io/) platform.

- <http://dev.bitly.com/organization_metrics.html>
    + None endpoints are implemented here, because all are premium. Contact me if you need it. 

- Lastly, sometimes, only a **small subset of input paramaters** has been implemented. Again contact me and I will consider a change. 

### What has been implemented for Goo.gl:

I believe everything. If not, let you me know.

