---
title: "Tutorial for RBitly"
author: "dmpe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial for RBitly}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package allows you to download your data and many useful statistics from [Bit.ly](https://www.bit.ly) account. To begin with, there is one requirement and that is to gain your API Key - or in the speech of the company - "Generic Access Token". 

## Authentication

For that there are **two ways**. The first one is to go to <https://bitly.com/a/oauth_apps> and generate one yourself. Then you will need to execute `rbitlyApi("Your Generic Access Token")` method. This is a **requirenment** to work with all functions in this package. 

Or (e.g. when you are lazy etc.) by using your username and password you can automatically acquire and set your API Key. Meaning you can execute `rbitlyApi_up("YourUsername", "YourPassword")` which not only will get your API Key (just in the case you will need it) but also, using the method above, "store" it R. 

Either one is OK. Choose the one which is more convenient to you. 


## An Example for User Metrics

First of all see here <http://dev.bitly.com/user_metrics.html>. Beware not all methods are implemented. To see which ones are, please read `ReadMe.md` file (and file an issue <https://github.com/dmpe/rbitly/issues>).

This returns my most-clicked Bit.ly links (ordered by number of clicks) in a given time period.

```{r}
library(RBitly)
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")

user.metrics.popular_links(unit = "month", units = -1, limit = 100)
```


## An Example for Link Metrics

First of all see here <http://dev.bitly.com/link_metrics.html>. All methods are implemented here!

This returns users who have encoded `http://bit.ly/DPetrov` link sorted by the number of clicks on each encoding user's link.

```{r}
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")
link.metrics.encoders_by_count(link = "http://bit.ly/DPetrov", my_network = "false", limit = 100)
```


## An Example for User Info/History

First of all see here <http://dev.bitly.com/user_info.html>. Beware not all methods are implemented. 

The first method returns an information about myself, whereas the second one returns a list of tracking domains I have configured (I have none).

```{r}
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")
user.info()

user.tracking_domain_list()
```


## An Example for Domains

First of all see here <http://dev.bitly.com/domains.html>. Beware not all methods are implemented. 

This will query whether a given domain is a valid bitly pro domain (nyti.ms is). 

```{r}
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")
bitly_pro_domain(domain = "nyti.ms")
```


-----------------
### What has (not) been implemented:

Based on <http://dev.bitly.com/>

<http://dev.bitly.com/user_info.html>  | Implemented Yes/No
------------- | -------------
/v3/oauth/app  | (**NOT**, see below)
/v3/user/info  | Yes
/v3/user/link_history | Yes
/v3/user/network_history  | (**NOT**)
/v3/user/tracking_domain_list  | Yes

<http://dev.bitly.com/link_metrics.html>  | Implemented Yes/No
------------- | -------------
/v3/link/clicks  | Yes
/v3/link/countries  | Yes
/v3/link/encoders  | Yes
/v3/link/encoders_by_count  | Yes
/v3/link/encoders_count  | Yes
/v3/link/referrers  | Yes
/v3/link/referrers_by_domain  | Yes
/v3/link/referring_domains  | Yes


<http://dev.bitly.com/user_metrics.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/user/clicks  | Yes 
/v3/user/countries  | Yes 
/v3/user/popular_earned_by_clicks  | No  | Yes
/v3/user/popular_earned_by_shortens  | No  | Yes
/v3/user/popular_links  | Yes
/v3/user/popular_owned_by_clicks  | No  | Yes
/v3/user/popular_owned_by_shortens | No  | Yes
/v3/user/referrers  | Yes
/v3/user/referring_domains | Yes
/v3/user/shorten_counts | Yes


<http://dev.bitly.com/domains.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/bitly_pro_domain  | Yes| No
/v3/user/tracking_domain_clicks  | No | Yes (cannot do unless sombody helps)
/v3/user/tracking_domain_shorten_counts  | No | Yes (cannot do unless sombody helps)


- <http://dev.bitly.com/links.html>
    + None endpoints are implemented here, because there is no use-case from my point of view. Per request can implement them, however. 
    
- <http://dev.bitly.com/nsq.html>  
    + None endpoints are implemented here, because all are premium. 
    
- <http://dev.bitly.com/organization_metrics.html>
    + None endpoints are implemented here, because all are premium.

- At the moment **no OAuth support** -> only basic [HTTP Basic Authentication Flow](http://dev.bitly.com/authentication.html#basicauth), which requires `Generic Access Token` from <https://bitly.com/a/oauth_apps>

- Additionally, only a **small subset of input paramaters** has been implemented. 

