---
title: "Tutorial for urlshorteneR -- v4"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial for urlshorteneR}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console  
---

`urlshorteneR` wrapps 2 URL services [Bit.ly](https://bitly.com) and [is.gd/v.gd](https://is.gd). 
In order to begin shortening URLs and downloading usefull statistics about short links, you have to -- in the case of <http://bit.ly> -- authenticate using OAuth2.0. 

For is.gd/v.gd there is no authentication needed. 

# Bit.ly

## User/App Information & Authentication for Bit.ly

Return some basic information about my user on Bit.ly. Additionally, is my account a "premium" one?

```{r}
library("knitr")
library(urlshorteneR)

if(interactive()) {
  opts_knit$set(root.dir = "~/Documents/Documents2/R-package-urlshortener")
  bitly_token <- readRDS("tests/bitly_local_token.rds")

# You can register a new pair of keys yourself - but you can also use mine - an option which is also by default
# bitly_token <- bitly_auth(key = "be03aead58f23bc1aee6e1d7b7a1d99d62f0ede8", secret = "f9c6a3b18968e991e35f466e90c7d883cc176073")
# bitly_token <- bitly_auth()

  ui <- bitly_user_info(showRequestURL = TRUE)
  is_bitly_user_premium_holder()
}
```

We can also decide to update my username with a different one.

```{r}
if (interactive()) {
bitly_update_user(name = "John Malc", showRequestURL = TRUE)
}
```

And what about the metadata about our OAUTH application?

```{r}
if (interactive()) {
bitly_app_details()
}
```

## Group Information

This retrieves information about a single group that user belongs to and and then about all groups that user are associated with. 

```{r}
if (interactive()) {

bitly_retrieve_group(ui$default_group_guid)
bitly_retrieve_groups()
}
```


## Information about Organizations

Official API documentation <https://dev.bitly.com/v4/#tag/User>. 

The first method returns an information about myself.

```{r}
if (interactive()) {
bitly_user_info()
}
```


### Custom Bitlinks

```{r}
if (interactive()) {
  df <- data.frame(pubDate = rep("2016-02-10", 4),
                   link = c("http://wwaaw.opencasdoesione.gov.it/progetti/1misepac01_000443/",
                            "http://wwssw.opencasdoesione.gov.it/progetti/1misepac01_000031/"),
                   stringsAsFactors = FALSE)
  df
  
  fin = NULL
  for (p in 1:length(df$link)) {
    fin[[p]] <- bitly_create_bitlink(long_url = df$link[p])
  }
}
```

**BEWARE:** This will proceed only with the two real links, not with the NA, NULL or an empty strings. 
These, however, will stop the flow of the code (i.e. are errors). 


# Is.gd & V.gd 

## Is.gd

```{r}
isgd_LinksShorten(longUrl = "http://cnn.com/", showRequestURL = TRUE)
```


## V.gd

```{r}
vgd_LinksShorten(longUrl = "http://cbs.com/", showRequestURL = TRUE)
```

