---
title: "Tutorial for RBitly"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial for RBitly}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package is wrapping [Bit.ly](https://www.bit.ly) API. In order to begin downloading usefull statistics about your Bit.ly links, there is one requirement, which is to gain your API Key (no OAuth support at this time) - so-called "Generic Access Token". 

## Authentication

For that there are **two ways**. 

1. The first one is to go to <https://bitly.com/a/oauth_apps> and generate one yourself. Then you will need to execute `rbitlyApi("Your Generic Access Token")` method. This is a **requirenment** to work with all functions in this package. 

2. **Or** you can retrieve your "Generic Access Token" using your username and password to the account which automatically sets your API Key. Meaning you can execute `rbitlyApi_up("YourUsername", "YourPassword")` which not only will print your API Key (just in the case you will need it) but also, using the method above, "store" it R. 

Either one is OK. Choose the one which is more convenient to you. 


## An Example for User Metrics

Official API documentation <http://dev.bitly.com/user_metrics.html>.

Method below returns my most-clicked Bit.ly links (ordered by number of clicks) in a given time period.

```{r}
library(RBitly)
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")

user_Metrics_PopularLinks(unit = "month", units = -1, limit = 100)
```


## An Example for Link Metrics

Official API documentation <http://dev.bitly.com/link_metrics.html>.

This returns users who have encoded `http://bit.ly/DPetrov` link sorted by the number of clicks on each encoding user's link.

```{r}
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")
link_Metrics_EncodersByCount(link = "http://bit.ly/DPetrov", my_network = "false", limit = 100)
```


## An Example for User Info/History

Official API documentation <http://dev.bitly.com/user_info.html>. 

The first method returns an information about myself, whereas the second one returns a list of tracking domains I have configured (I have none).

```{r}
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")
user_Info()

user_TrackingDomains()
```


## An Example for Domains

Official API documentation <http://dev.bitly.com/domains.html>. 

This will query whether a given domain is a valid Bit.ly PRO domain (nyti.ms is). 

```{r}
rbitlyApi("0906523ec6a8c78b33f9310e84e7a5c81e500909")
bitly_pro_domain(domain = "nyti.ms")
```

-------------

### What has (not) been implemented:

Based on <http://dev.bitly.com/>

<http://dev.bitly.com/user_info.html>  | Implemented Yes/No
------------- | -------------
/v3/oauth/app  | (**NOT**, see below)
/v3/user/info  | Yes
/v3/user/link_history | Yes
/v3/user/network_history  | **NOT**
/v3/user/tracking_domain_list  | Yes

<http://dev.bitly.com/link_metrics.html>  | Implemented Yes/No
------------- | -------------
/v3/link/clicks  | Yes
/v3/link/countries  | Yes
/v3/link/encoders  | Yes
/v3/link/encoders_by_count  | Yes
/v3/link/encoders_count  | Yes
/v3/link/referrers  | Yes
/v3/link/referrers_by_domain  | Yes
/v3/link/referring_domains  | Yes


<http://dev.bitly.com/user_metrics.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/user/clicks  | Yes 
/v3/user/countries  | Yes 
/v3/user/popular_earned_by_clicks  | **NOT**  | Yes
/v3/user/popular_earned_by_shortens  | **NOT**  | Yes
/v3/user/popular_links  | Yes
/v3/user/popular_owned_by_clicks  | **NOT**  | Yes
/v3/user/popular_owned_by_shortens | **NOT**  | Yes
/v3/user/referrers  | Yes
/v3/user/referring_domains | Yes
/v3/user/shorten_counts | Yes


<http://dev.bitly.com/domains.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/bitly_pro_domain  | Yes | No
/v3/user/tracking_domain_clicks  | **NOT** | Yes (cannot do unless sombody helps)
/v3/user/tracking_domain_shorten_counts  | **NOT** | Yes (cannot do unless sombody helps)


<http://dev.bitly.com/links.html> | Implemented Yes/No | Premium
------------- | ------------- | -------------
/v3/expand  | Yes 
/v3/info  | Yes 
/v3/link/lookup  |  Yes
/v3/shorten  | Yes  
/v3/user/link_edit  | **NOT**  | No
/v3/user/link_lookup  | **NOT**  | No
/v3/user/link_save | **NOT**  | No
/v3/user/save_custom_domain_keyword | **NOT**  | Yes



- <http://dev.bitly.com/nsq.html>  
    + None endpoints are implemented here, logically, because all are "premium". Addionally, this is only for the [NSQ](http://nsq.io/) platform.
    
- <http://dev.bitly.com/organization_metrics.html>
    + None endpoints are implemented here, because all are premium. Contact me if you need it. 

- At the moment **no OAuth support** is present so that one must use [HTTP Basic Authentication Flow](http://dev.bitly.com/authentication.html#basicauth), which requires `Generic Access Token` from <https://bitly.com/a/oauth_apps> (see above).

- Lastly, sometimes, only a **small subset of input paramaters** has been implemented. Again contact me and I will consider a change. 

