---
title: "Tutorial for urlshorteneR"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial for urlshorteneR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
This package wrapps [Bit.ly](https://bitly.com). In order to begin shortening URLs and downloading usefull statistics, there is one requirement, which is to authenticate using OAUTH2 for each service (of course, if you need both of them) 
  
## Authentication

See `??googl_auth`. Please do not use my API Keys as they may not work properly. 
  
# Bit.ly
  
## An Example for User Metrics
  
Official API documentation <http://dev.bitly.com/user_metrics.html>.
  
Method below returns my most-clicked Bit.ly links (ordered by number of clicks) in a given time period.
  
```{r}
library(urlshorteneR)
# print(getwd())
# 
# btoken_path <- file.path("..", "tests", "testthat", "bitly_token.rds")

if (interactive()) {

bitly_token <- readRDS("../tests/testthat/bitly_token.rds")

# You can register a new pair of keys yourself - but you can also use mine. 
# bitly_token <- bitly_auth(key = "be03aead58f23bc1aee6e1d7b7a1d99d62f0ede8", secret = "c7eb384b2f4ce4b109fe616f1c9455e4f7735917")

bitly_UserMetricsPopularLinks(unit = "month", units = -1, limit = 100)
}
```


## An Example for Link Metrics

Official API documentation <http://dev.bitly.com/link_metrics.html>.

This returns users, who have encoded `http://bit.ly/DPetrov` link sorted by the number of clicks on each encoding user's link.

```{r}
if (interactive()) {

bitly_LinksMetricsEncodersByCount(link = "http://bit.ly/DPetrov", my_network = "false", limit = 100)
}
```


## An Example for User Info/History

Official API documentation <http://dev.bitly.com/user_info.html>. 

The first method returns an information about myself, whereas the second one returns a list of tracking domains I have configured (I have none).

```{r}
if (interactive()) {

bitly_UserInfo()

bitly_UserTrackingDomains()
}
```


## An Example for Domains

Official API documentation <http://dev.bitly.com/domains.html>. 

This will query whether a given domain is a valid Bit.ly PRO domain (nyti.ms is). 

```{r}
if (interactive()) {

bitly_IsProDomain(domain = "nyti.ms")
}
```

```

# Is.gd

```{r}
isgd_LinksShorten(longUrl = "http://debil.cz/", showRequestURL = TRUE)
```


-------------
